Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-01 paper/paper.qmd
update paper

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using unweighted fitted Linear Model"
#| label: fig-support-trend1
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ candidate,ncol = 2) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",caption = 
                   "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using weighted fitted Linear Model"
#| label: fig-support-trend2
# Plotting with the filtered data
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ candidate,ncol = 2) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red"))  +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Unweighted Fitted Linear Model"
#| label: fig-support-respondent1
custom_labels <- c("lv" = "Likely Voters", "rv" = "Registered Voters")
### unweighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Weighted Fitted Linear Model"
#| label: fig-support-respondent2
### weighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Fitted Linear Model"
#| label: fig-support-state
## unweighted
selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
combined_data_total<-combined_data_total|>filter(state %in% selected_states)
combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Weighted Fitted Linear Model"
#| label: fig-support-state2
## weighetd
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

@@

Harris model: RMSE of 3.42, indicating an average prediction error of
around 3.44 percentage points.\
Trump model: RMSE of 4.30, showing a slightly higher prediction error on
average.\

R-squared: Represents the proportion of the variance in the response
variable explained by the model (higher is better).\
Harris model: R-squared of 0.33, meaning the model explains about 34.6%
of the variance in Harris's polling data.\
Trump model: R-squared of 0.27 as well, indicating similar explanatory
power for Trump's polling data.

MAE (Mean Absolute Error): Shows the average absolute difference between
observed and predicted values (lower is better).\
Harris model: MAE of 2.48, meaning that, on average, the predictions are
off by 2.48 percentage points.\
Trump model: MAE of 3.15, indicating slightly less precise predictions
compared to the Harris model.\

Interpretation Summary Predictive Accuracy: The Harris model has
slightly better predictive accuracy than the Trump model, as reflected
by its lower RMSE and MAE values.\
Model Fit: Harris' model explain roughly 33% of the variance in their
respective datasets. Trump's models explain roughly 33% of the variance
in their respective datasets.This suggests that other factors not
included in the model may play a significant role in explaining the
remaining variance.\
This summary indicates the models are moderately predictive, with room
for improvement in accuracy and fit, potentially by adding more
predictors or adjusting model specifications.\

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using unweighted fitted Linear Model"
#| label: fig-support-trend1
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+
  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",caption = 
                   "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using weighted fitted Linear Model"
#| label: fig-support-trend2
# Plotting with the filtered data
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+
  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red"))  +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Unweighted Fitted Linear Model"
#| label: fig-support-respondent1
custom_labels <- c("lv" = "Likely Voters", "rv" = "Registered Voters")
### unweighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Weighted Fitted Linear Model"
#| label: fig-support-respondent2
### weighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Fitted Linear Model"
#| label: fig-support-state
## unweighted
selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
combined_data_total<-combined_data_total|>filter(state %in% selected_states)
combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Weighted Fitted Linear Model"
#| label: fig-support-state2
## weighetd
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

## Predicted Support for Harris and Trump by Major Pollsters
```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by Pollster using Unweighted Fitted Linear Model"
#| label: fig-support-pollster1

# Calculate the top 10 pollsters by frequency in the data
top_pollsters <- combined_data_total %>%
  count(pollster) %>%
  top_n(5, n) %>%
  pull(pollster)

# Create a new variable to label the top pollsters and others as "Other"
combined_data_total <- combined_data_total %>%
  mutate(pollster_group = ifelse(pollster %in% top_pollsters, as.character(pollster), "Other"))

ggplot(combined_data_total, aes(x = end_date, y = pct, size = combined_weight)) +
  geom_point(aes(fill = pollster_group), alpha = 0.5, shape = 21, color = "black") + 
  geom_line(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
            aes(x = end_date, y = predicted_unweighted), color = "blue", size = 1) +
  geom_line(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
            aes(x = end_date, y = predicted_unweighted), color = "red", size = 1) +
  facet_wrap(~ candidate, ncol = 2) +
  labs(
    title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election by Top 5 Pollster \n(From August 1, 2024 to October 27, 2024)",
    subtitle = "predicted using weighted multiple linear regression model",
    x = "End Date of the Poll",
    y = "Predicted Support (%)",
    size = "Weight",
    fill = "Pollster",
    caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population"
  ) +
  scale_fill_manual(values = c(setNames(rep("grey", length(unique(combined_data_total$pollster_group))), "Other"),
                               setNames(rainbow(10), top_pollsters))) + # Assign colors to top pollsters and grey to others
  theme_classic() +
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",  # Place legends in a horizontal row
    legend.title.align = 0.5,   # Center-align legend titles for better appearance
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.background = element_rect(colour = "black", fill = "white")
  ) +
  guides(
    size = guide_legend(order = 1, title.position = "top", label.position = "left"),
    fill = guide_legend(order = 2)
  ) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by Pollster using Weighted Fitted Linear Model"
#| label: fig-support-pollster2

ggplot(combined_data_total, aes(x = end_date, y = pct, size = combined_weight)) +
  geom_point(aes(fill = pollster_group), alpha = 0.5, shape = 21, color = "black") + 
  geom_line(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
            aes(x = end_date, y = predicted_weighted), color = "blue", size = 1) +
  geom_line(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
            aes(x = end_date, y = predicted_weighted), color = "red", size = 1) +
  facet_wrap(~ candidate, ncol = 2) +
  labs(
    title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election by Top 5 Pollster \n(From August 1, 2024 to October 27, 2024)",
    subtitle = "predicted using weighted multiple linear regression model",
    x = "End Date of the Poll",
    y = "Predicted Support (%)",
    size = "Weight",
    fill = "Pollster",
    caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population"
  ) +
  scale_fill_manual(values = c(setNames(rep("grey", length(unique(combined_data_total$pollster_group))), "Other"),
                               setNames(rainbow(10), top_pollsters))) + # Assign colors to top pollsters and grey to others
  theme_classic() +
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",  # Place legends in a horizontal row
    legend.title.align = 0.5,   # Center-align legend titles for better appearance
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.background = element_rect(colour = "black", fill = "white")
  ) +
  guides(
    size = guide_legend(order = 1, title.position = "top", label.position = "left"),
    fill = guide_legend(order = 2)
  ) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))

@@

Harris model: RMSE of 3.41, indicating an average prediction error of
around 3.44 percentage points.\
Trump model: RMSE of 4.28, showing a slightly higher prediction error on
average.\

R-squared: Represents the proportion of the variance in the response
variable explained by the model (higher is better).\
Harris model: R-squared of 0.34, meaning the model explains about 34.6%
of the variance in Harris's polling data.\
Trump model: R-squared of 0.28 as well, indicating similar explanatory
power for Trump's polling data.

MAE (Mean Absolute Error): Shows the average absolute difference between
observed and predicted values (lower is better).\
Harris model: MAE of 2.40, meaning that, on average, the predictions are
off by 2.48 percentage points.\
Trump model: MAE of 3.09, indicating slightly less precise predictions
compared to the Harris model.\

Interpretation Summary Predictive Accuracy: The Harris model has
slightly better predictive accuracy than the Trump model, as reflected
by its lower RMSE and MAE values.\
Model Fit: Harris' model explain roughly 34% of the variance in their
respective datasets. Trump's models explain roughly 28% of the variance
in their respective datasets.This suggests that other factors not
included in the model may play a significant role in explaining the
remaining variance.\
This summary indicates the models are moderately predictive, with room
for improvement in accuracy and fit, potentially by adding more
predictors or adjusting model specifications.\
